### 2015-10-16 manuscript.Rnw
add conclusion

\section{Conclusion}
\label{sec:conclusion}

Resource as useful as the data that is in it. To make data available, it needs
to follow conventions so it can be incorporated into the OTL, i.e., submit tree
files (not images) to public repositories.

OTL provides an easy-to-use interface to submit studies.

>>>>

\section{Concluding remarks}
\label{sec:conclusion}

The recognition of the importance of phylogenies to account for the statistical
non-independence of species in comparative methods, and the recent development
of methods to explore trait evolution or changes in diversification rates have
driven the need for accurate phylogenies. However, there is often a discrepancy
between taxa targeted by comparative methods, and taxa for which phylogenies are
available. We believe that by providing an easy-to-use interface to obtain
phylogenies for an arbitrary set of taxa directly in R, \texttt{rotl} will be
useful in a wide variety of contexts.

The accuracy and usefulness of the data provided by OTL relies on the community
to make generated phylogenies (and their metadata) digitally available as tree
files (i.e., Newick, NEXUS or NeXML). We strongly encourage researchers to
submit their published phylogenies to OTL using the curator interface
\url{https://tree.opentreeoflife.org/curator}. By facilitating the discovery and
re-use of published trees and of the synthetic tree, we hope \texttt{rotl} will
contribute to the wider adoption of best practices to make phylogenetic
information available and re-usable.
